%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\input{glyphtounicode}
\pdfgentounicode=1

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://colinfike.github.io/}{\Large Colin Fike}} & Email : \href{mailto:colin.fike@gmail.com}{colin.fike@gmail.com}\\
  \href{https://colinfike.github.io/}{https://colinfike.github.io/} & Mobile : 716-523-8130 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dictionary.com}{San Francisco, CA}
      {Backend Engineer}{July 2018 - December 2019}
      \resumeItemListStart
        %\resumeItem{Lexicographical Content APIs}
         % {Created/maintained Node.js APIs that serve lexicographical content to front end applications at rates of 100-200 requests per second while minimizing infrastructural overhead.}
         \resumeItem{Mobile API}
          {Implement a mobile API serving 100-200 requests per second by manipulating legacy data sources and reverse engineering legacy markup/formatting to enable complete migration off legacy PHP monolith.}
         \resumeItem{Content Ingestion Pipeline}
          {Design/Implement a pipeline to transform independent XML sources into a common graph form resulting in ability to publish new dictionary content and generate data relationships. }
         \resumeItem{Fastly Custom VCL}
          {Achieved a 85-90\% hit rate across 12 properties receiving {\raise.17ex\hbox{$\scriptstyle\sim$}}4000 requests per second using custom VCL to route/cache all requests. Owner of all Fastly configurations.}
          \resumeItem{AWS Infrastructure}
          {Maintained and created the infrastructure on AWS including Elastic Beanstalks, CloudWatch, Lambdas, Kinesis, and others. Optimized operational costs and availability via auto scaling tuning.}
         \resumeItem{Header Bidding}
          {Created package to enable header bidding with Pubmatic via new Google first price bidder to maintain existing ad revenue. Wrote low latency code for real time markup of bids to optimize ad revenue.}
         \resumeItem{CI/CD Pipelines}
          {Utilized Docker image caching and mirroring to enable ability to test/deploy code within minutes via Gitlab CI Runners building production Docker images for deploy to Elastic Beanstalks.}
         \resumeItem{MongoDB Clusters}
          {Processed greylist/whitelist on {\raise.17ex\hbox{$\scriptstyle\sim$}}19 million example sentences and restored to production in zero downtime deployment. Managed clusters that provided thesaurus and dictionary data to APIs.}
         \resumeItem{Mentorship}
          {Mentor less experienced coworkers via pair programming, peer code review, and presentations.}
      \resumeItemListEnd

    \resumeSubheading
      {Chewse}{San Francisco, CA}
      {Full Stack Engineer}{May 2017 - March 2018}
      \resumeItemListStart
        \resumeItem{Self-Service Prix Fixe Meal Checkout}
          {Implemented new checkout flow that enables users to browse, schedule, and purchase a meal without having to go through customer support with Django/Vue.js. Reduce time to schedule a meal from a day or more to several minutes.}
        \resumeItem{Client Facing Frontend/Backend Redesign}
          {Implement new meal calendar, adhoc order requests, dynamic feedback forms, and other pages in new framework, Vue.js. Create/Update APIs to support new frontend functionality. Streamline frontend and reduce load time for clients to see scheduled meals by 75\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Mainstreet Computing}{Buffalo, NY}
      {Full Stack Engineer}{Fall 2014 - February 2017}
      \resumeItemListStart
        \resumeItem{Insurance Application Processing Proxy}
          {Lead development of proxy service that consumed an insurance application payload in JSON format, dynamically navigated the Healthcare.gov application, and saved the result of the application in PDF format using Ruby on Rails.}
        \resumeItem{Creative Manager and Live Editor}
          {Lead development of web app allowing clients to create campaigns and creative ad units that could be previewed and have assets modified on the fly through scoping, tasking, and programming roles using Ruby on Rails and Javascript.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo, SUNY}{Buffalo, NY}
      {Bachelor of Science in Computer Science;  GPA: 3.582 }{Fall. 2010 -- Dec. 2014}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/colinfike/yougo-premium}{YougoPremium}}
      {Command line tool written in Go used to subscribe to YouTube channels and download latest videos since the last download to your local machine for offline playback.}
    \resumeSubItem{\href{https://github.com/colinfike/judgego}{JudgeGo}}
      {Personal Discord bot written in Go with functionality to create sound clips from YouTube videos, sound clip playback via voice channels, Markov chain and sentence generation from user message history, and moderate channels.}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Node.js, Go, VCL, Python/Django, Ruby/Rails, SQL, CSS/HTML}
    \resumeSubItem{Technologies}
      {Docker, Fastly, AWS, MongoDB, Redis, Terraform, React, Heroku, ElasticSearch/Kibana, Unix }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
% \resumeSubHeadingListStart
%   \item{
%    \textbf{Languages}{: Javascript, Go, Python, Ruby, SQL, CSS/HTML}
%    \hfill
%    \textbf{Technologies}{: Docker, AWS, Mongo, Cypher, React, Heroku, Apache }
%}
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}